Observing Economic Growth in Unrecognized States with Nighttime Light \thanks{I thank Elizaveta Kugaevskaia for her superb research assistance on this project. Financial support from Japan Society for the Promotion of Science (JSPS Kakenhi Grant Number 17K13730) is gratefully acknowledged.}

### 2019-03-18 paper/paper.tex
Minor revision in Introduction #54 #56

The empirical challenge for such endeavor is the lack of data. International organizations such as the World Bank do not provide any data for unrecognized states. 
The limited state capacity of these territories implies that there is no official statistics. 
Any surveys conducted in their parent countries exclude these territories from the sampling procedure.%
\footnote{%
	As an example, the Demographic and Health Survey conducted in Moldova in 2005 excludes the entire Transnistria from its sample (National Scientific and Applied Center for Preventive Medicine 2006: xxvi).
} 
To overcome this data limitation, the present study uses the satellite images of nighttime light for the period 1993--2013 to recover the unobserved annual economic growth rates of the four unrecognized states in the former Soviet Union.

@@

Second, the issue of unrecognized states has been ignored by the emerging literature on the impacts of civil conflicts%
\footnote{
	See Blattman and Miguel (2010: Section 4) and Bauer et al.\ (2016) for surveys.
}  
even though the lack of international recognition is one of the likely consequences from those civil wars in which one side attempts to secede from the parent country. 
By filling this gap in the literature, our study makes two contributions.

>>>>

The empirical challenge for such endeavor is the lack of data. International organizations such as the World Bank do not provide any data for unrecognized states. 
The limited state capacity of these territories implies that there is no official statistics. 
Any surveys conducted in their parent countries exclude these territories from the sampling procedure.%
\footnote{%
	As an example, the Demographic and Health Survey conducted in Moldova in 2005 excludes the entire Transnistria from its sample (National Scientific and Applied Center for Preventive Medicine 2006:xxvi).
} 
To overcome this data limitation, the present study uses the satellite images of nighttime light for the period 1993--2013 to recover the unobserved annual economic growth rates of the four unrecognized states in the former Soviet Union.

@@

Second, the issue of unrecognized states has been ignored by the emerging literature on the impacts of civil conflicts%
\footnote{
	See Blattman and Miguel (2010:Section 4) and Bauer et al.\ (2016) for surveys.
}  
even though the lack of international recognition is one of the likely consequences from those civil wars in which one side attempts to secede from the parent country. 
By filling this gap in the literature, our study makes two contributions.
